Bee brain size is positively associated with urban lifestyles but not with positive population trends

### 2022-11-27 Manuscript/Ms.Rmd
methods update

@@

### Habitat preference

@@

### Encephalisation

We estimated brain size relative to the body (i.e., encephalisation) by modeling the log-transformed association between brain weight and intertegular span. For this, we specified a simple Bayesian regression with the function *brm* from the package *brms* version xxxx where brain weight was the response variable and intertegular span the predictor.

brain weight was the response variable and intertegular span the predictor.

### Modelling

>>>>

We constructed a phylogeny with all studied species by using a previously published genus-level bee phylogeny [@hedtke2013].

@@

**(i) Habitat preference**

@@

**(ii) Encephalisation**

We estimated brain size relative to the body (i.e., encephalisation) by modeling the log-transformed association between brain weight and intertegular span. For this, we specified a simple Bayesian regression with the function *brm* from the package *brms* version 2.18 [@burkner2017] where brain weight was the response variable and intertegular span the predictor. To correct for the non-independent evolutionary histories among species, we included the phylogenetic covariance matrix as random factor. The model was run with 4,000 iterations with previous 1,000 warm up iterations and with non or very weakly informative priors from the brm function so the priors had negligible influence on the results [@burkner2017]. After conducting the posterior predictive checks with the function *pp_check* from *brms*, we extracted the residuals that represented species encephalisation.

**(iii) Habitat preference ~ encephalisation**
